Untitled

### 2017-08-23 PaperCode.Rmd
Unaffordability
Fixed the AUX code so that Income is loaded. Added in the unnaffordability section

@@

@@

#The model that uses easily available data is 3% less accurate than the other model.
t.test(ModelStats2$Accuracy, ModelStats1$Accuracy)

@@

set.seed(1983)
MultiCheck <- 1:21 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

@@

@@

BinomSimp <- glm(Reference~ price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)

@@

confusionMatrix(predict(BinomSimp, ModelMe, type = "response")>0.5 , ModelMe$Reference)

@@

#random forest appears better than multilinear but when checked on many resamples it is worse... how? To much noise?
EnglandComp <- LADDep %>% 
  select (LAD11CD, LAD11NM = Local.Authority.District.name..2013., Extent)%>% 
  left_join(., Vacants, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD" = "Admin_district_code")) %>%
  left_join( LadHomes, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes) %>%
  mutate(Significant.Competition = predict(BinomExtent, ., type = "response")) %>%
  mutate(Comp.Type = case_when(
    .$Significant.Competition<0.5-tol ~"No",
    .$Significant.Competition>0.5 + tol ~"Yes",
    .$Significant.Competition>0.5-tol & .$Significant.Competition<0.5+tol ~"Borderline"
  ))

@@

@@

>>>>

#Look at saleries
```{r}

unafford <- ls(pattern = "DATA") %>%
  map_df(~get(.x) %>% select(LowUse:WardLowuseClass)) %>%
  group_by(MSOA11CD) %>%
  summarise(LowUse = sum(LowUse, na.rm = T),
            Homes = sum(Homes, na.rm = T),
            Pop = sum(Pop, na.rm = T)) %>%
  mutate(LowUsePerc = LowUse/Homes) %>%
  left_join(IncomeEst, by = "MSOA11CD") %>%
  mutate(decile = ntile(ratio, 20))

unaffordExLon <- unafford %>%
  filter(Region.name != "London") %>%
  mutate(decile = ntile(ratio, 50))

#London follows the same pattern it just happens further up the scale
unaffordLon <- unafford %>%
  filter(Region.name == "London") %>%
  mutate(decile = ntile(ratio, 50))

cor(unaffordExLon$LowUsePerc, unaffordExLon$ratio)
cor(unaffordExLon$LowUsePerc, unaffordExLon$MedianPrice)
cor(unaffordExLon$Yearly.income, unaffordExLon$MedianPrice)
cor(unafford$Yearly.income, unafford$MedianPrice, "complete.obs")

test <- lm(MedianPrice ~ LowUsePerc + Yearly.income, data  = unafford)

#This is no Longer useful due to using the whole percentile range 
# test <- 2:50 %>% 
#   map_df(~{
#   decile <- unaffordExLon %>%
#     mutate(decilev = ntile(ratio, .x)) %>%
#     filter(decilev == 1 | decilev == .x) %>%
#     group_by(decilev) %>%
#     summarise(mean = mean(LowUsePerc)) %>%
#     mutate(group = .x) %>%
#     spread(key = decilev, value = mean) %>%
#     setNames(c("group", "LowMean", "HighMean"))
#   
# }) 
# 
# test %>%
#   gather(key = type, value = mean, -group)%>%  
#   ggplot(aes(x = type, y = mean )) + geom_boxplot()
# 
# 
# test %>%
#   gather(key = type, value = mean, -group)%>% 
#   ggplot(aes(x = group, y = mean, colour = type )) + geom_point()
# 
# 
# test2 <- test %>%
#   mutate(ratio = HighMean/LowMean) 
# test2 %>%
#   ggplot(aes(x = group, y = ratio,)) + geom_point()
# 
# cor(test2$ratio, test2$group)

decile <- bind_rows(mutate(unaffordExLon, type = "Excl London"), 
                    mutate(unafford, type = "Inc London"),
                    mutate(unaffordLon, type = "London")) %>%
    group_by(type) %>%
    mutate(decile = ntile(ratio, 50)) %>%
      group_by(decile, type) %>%
    summarise(mean = mean(LowUsePerc),
              median = median(LowUsePerc),
              counts = n()
              )

#Looking at the relationship between unaffordability and LUP percentage

decile %>% ggplot() + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(x= decile, y = median, colour = type))

#Example of the theoretical relationship

data_frame(Index = 1:100) %>%
  mutate(Primary = exp(-0.05*(Index))+0.05, 
         Auxilary = (exp(Index/100)-1),
    Total = Primary + Auxilary) %>%
  gather(key = "Type", value = "value", -Index) %>%
  ggplot(aes(x= Index, y = value, colour = Type )) +
  geom_point() +
  labs(title = "LUP percentage as a function of primary and Auxilary demand",
       x = "Demand",
       y = "LUP percentage") +
  theme(
  axis.text.x = element_blank(),
  axis.text.y = element_blank()
  )

@@

Rural Urban split
```{r}
setwd(DataFolder)

Rural <- read_csv( "RUC11_LAD11_ENv2.csv" )[-1,] %>%
  setNames(make.names(names(.))) %>%
  rename(PercRural = Rural.including.hub.towns..rural...rural.related..population1_1) %>%
  select(LAD11CD, PercRural) %>%
  mutate(PercRural = as.numeric(PercRural))

#Update Gateshead and Northumberland Codes
Rural$LAD11CD[Rural$LAD11CD == "E08000020"] <-"E08000037"
Rural$LAD11CD[Rural$LAD11CD == "E06000048"] <- "E06000057"

Combine1ExO <- Combine1ExO %>%
  left_join(Rural, by = "LAD11CD")

@@

#The model that uses easily available data is 3% less accurate than the other model.
t.test(ModelStats2$Accuracy, ModelStats3$Accuracy)

@@

#Linear
set.seed(1983)
MultiCheck <- 1:21 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

@@

#Tree
set.seed(1983)
MultiCheck <- 1:111 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

  model <- rpart(Reference~ Extent + price + VacantsPerc+ PercRural,data=as.data.frame(TestResample))

  data_frame(x = predict(model, ModelMe, type = "prob")[,2]>0.5) %>%
    setNames(paste("Model", .x, sep="_"))
}
) %>% bind_cols() %>% 
  mutate(
  Outcome = case_when(
  rowSums(.)>ncol(.)/2 ~TRUE,
  rowSums(.)<=ncol(.)/2 ~FALSE
))

@@

@@

@@

#random forest appears better than multilinear but when checked on many resamples it is worse... how? To much noise?
EnglandComp <- LADDep %>% 
  select (LAD11CD, LAD11NM = Local.Authority.District.name..2013., Extent)%>% 
  left_join(., Vacants, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD" = "Admin_district_code")) %>%
  left_join( LadHomes, by = "LAD11CD") %>%
  left_join(Rural, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes)

#Preds <- predict(BinomExtent, EnglandComp , type = "response")
set.seed(1983)
Preds <- 1:111 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

  model <- rpart(Reference~ Extent + price + VacantsPerc,data=as.data.frame(TestResample))

  data_frame(x = predict(model, EnglandComp, type = "prob")[,2]>0.5) %>%
    setNames(paste("Model", .x, sep="_"))
}
) %>% bind_cols() %>% 
  mutate(
  Outcome = rowSums(.)/ncol(.))

EnglandComp <- EnglandComp%>% 
  left_join(select(ModelMe, LAD11CD, Reference), by = "LAD11CD") %>%
  mutate(
    Significant.Competition = ifelse(is.na(Reference),
                                     unlist(Preds$Outcome), 
                                     as.logical(Reference))
    ) %>%
  mutate(

      Comp.Type = case_when(
      .$Significant.Competition<0.5-tol ~"No",
      .$Significant.Competition>0.5 + tol ~"Yes",
      .$Significant.Competition>0.5-tol & .$Significant.Competition<0.5+tol ~"Borderline"
      )
  ) %>%
  select(-Reference)

@@

#Estimated

@@

#Observed
Combine1ExO %>%
  group_by((absdiff>0)) %>%
  summarise(mean = mean(HomePrice),
            median = median(HomePrice),
            Homes = sum(Homes),
            Pop = sum(Pop)) %>%
  mutate(HomesPerc = Homes/sum(Homes),
         PopPerc = Pop/sum(Pop))
